DSSynth: An Automated Digital Controller Synthesis Tool for Physical Plants

### 2017-08-16 ase2017/paper.tex
tt font
eucal
font tweaks

\usepackage{microtype}
\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{epstopdf} %converting to PDF
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{pgfplots}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983z^2 + 0.09587z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665z + 0.75
\end{lstlisting}
\vspace{-0.2cm}
\caption{Synthesis of a digital controller for the physical plant defined in Eq.(\ref{equation_plant}) in MATLAB, with a fixed-point format  $\left\langle 8,8\right\rangle$}
\label{toolbox-usage}
\end{figure}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = feedback(series(controller, plant),1)
>> sys =
>>        0.06863z^4 - 0.006591z^3 - 0.01324z^2
>> ---------------------------------------------------
>> 1.069z^4 - 1.136z^3 + 0.4849z^2 - 0.8704z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system using the series configuration as
illustrated in Fig.~\ref{fig:typical-control-system}}
\label{combine-controller-plant}
\end{figure}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,]
>> den = [1.069 -1.136 0.4849 -0.8704 0.5317]
>> r = roots(den)
>> r =
>>  -0.2912 + 0.8061i
>>  -0.2912 - 0.8061i
>>   0.8225 + 0.0219i
>>   0.8225 - 0.0219i
\end{lstlisting}
\vspace{-0.2cm}
\caption{Roots of the polynomial $D(z)$ given by Eq.~\ref{equation_general}.}
\label{roots-of-dz}
\end{figure}

>>>>

\usepackage{microtype}
\usepackage{xspace,framed}
\usepackage{listings}
\usepackage{graphicx}
\usepackage{epstopdf} %converting to PDF
\usepackage{subfig} 
\usepackage{xcolor,colortbl}
\usepackage{amssymb}
\usepackage{amsmath}
\usepackage{hyperref}
\usepackage{cite}	
\usepackage{mathtools}
\usepackage{tikz}
\usetikzlibrary{positioning, automata, shapes.arrows, calc, shapes, arrows}
\usetikzlibrary{patterns}
\usepackage{pgfplots}
\usepackage{inconsolata} % tt font
\usepackage{eucal}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,basicstyle=\tt]
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> system = tf(num,den,0.002);
>> y = synthesize(system,8,8,1,-1);
>> SYNTHESIS SUCCESSFUL
>> y = 
>>  -0.9983z^2 + 0.09587z + 0.1926
>>  --------------------------------
>>       z^2 + 0.5665z + 0.75
\end{lstlisting}
\caption{Synthesis of a digital controller for the physical plant
defined in Eq.~(\ref{equation_plant}) with 
fixed-point format $\left\langle 8,8\right\rangle$}
\label{toolbox-usage}
\end{figure}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single,basicstyle=\tt]
>> num = [-0.99832 0.09587 0.1926];
>> den = [1 0.5665 0.75];
>> controller = tf(num,den,0.002);
>> num = [-0.06875 0 0];
>> den = [1.0000 -1.696 0.7089];
>> plant = tf(num,den,0.002);
>> sys = feedback(series(controller, plant),1)
>> sys =
>>        0.06863z^4 - 0.006591z^3 - 0.01324z^2
>> ---------------------------------------------------
>> 1.069z^4 - 1.136z^3 + 0.4849z^2 - 0.8704z + 0.5317
\end{lstlisting}
\vspace{-0.2cm}
\caption{General equation for the closed-loop control system using the series configuration as
illustrated in Fig.~\ref{fig:typical-control-system}}
\label{combine-controller-plant}
\end{figure}

@@

\begin{figure}[ht]
\scriptsize
\begin{lstlisting}[xleftmargin=.025\textwidth,xrightmargin=.025\textwidth, frame=single, basicstyle=\tt]
>> den = [1.069 -1.136 0.4849 -0.8704 0.5317]
>> r = roots(den)
>> r =
>>  -0.2912 + 0.8061i
>>  -0.2912 - 0.8061i
>>   0.8225 + 0.0219i
>>   0.8225 - 0.0219i
\end{lstlisting}
\vspace{-0.2cm}
\caption{Roots of the polynomial $D(z)$ given by Eq.~\ref{equation_general}}
\label{roots-of-dz}
\end{figure}
